My title

### 2024-11-04 paper/paper.qmd
More discussion

As our paper is about the 2024 United States federal election and more specifically we are looking at the polls and the polling data comparing the two candidates, former President Donald Trump and Vice President Kamala Harris, for the upcoming election. Our original Data set had over 16,000 unique entries from different pollsters, the business or Organization that conducts the poll. Each poll has two entries, one giving the Data for the polling opinions of Donald Trump and the second for Kamala Harris. We have acquired our polling data from @fivethirtyeight2024

@@

We believe Arizona will vote: **IDK**

@@

We believe Georgia will vote: **Trump**

@@

Harris is currently leading the polls in Michigan with 48% of the vote and Trump with 43%, this is a rather significant margin.

@@

## Wisconsin {#sec-Wisconsin}

>>>>

As our paper is about the 2024 United States federal election and more specifically we are looking at the polling Data and the polling data comparing the two candidates, former President Donald Trump and Vice President Kamala Harris, for the upcoming election. Our original Data set had over 16,000 unique entries from different pollsters, the business or Organization that conducts the poll. Each poll has two entries, one giving the Data for the polling opinions of Donald Trump and the second for Kamala Harris. We have acquired our polling data from @fivethirtyeight2024

@@

We believe Arizona will vote: **Donald Trump**

@@

We believe Georgia will vote: **Donald Trump**

@@

Harris is currently leading the polls in Michigan with 49% of the vote and Trump with 47%, this is a rather slim margin, but the first in the discussed states where Harris is leading in the polls. In @fig-pollingharris we can see that there was a significant jump for Harris and a small dip in October followed by a gradual increase leading up to the elections. When we look at the voting history of the state in the last two elections, the have voted for the same candidates as Arizona and Georgia, where they voted for Biden in 2020 and for Trump in 2016, with the voting percentages at 50.6% to 47.8% in 2020 and 47.5% to 47.3 in 2016 with respect to the winner. Although unlike the previously mentioned states 2016 was the first time the state voted for the republican candidate since 1992. Considering Michigan is home to the largest black majority city in the United states, Detroit, and a large majority of union workers who often vote democratic as it is seen as the more union-friendly party between the two it is rather like that Harris will win the state.

We believe Michigan will vote for: **Kamala Harris**

@@

## Wisconsin {#sec-wisconsin}
